---
title: "Intro to tsortmusicr"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Intro to tsortmusicr}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(tsortmusicr)
```

This is a package designed to help explore data from the great website https://tsort.info/.

Note that usage of data from tsort.info is free under the following conditions:

1. Acknowledge the source.

2. Prominently link to https://tsort.info

3. Always include version number.


## Data import from tsort.info

The following functions to read data from tsort.info are available:

**tsm_read_songs()**: Wrapper around readr::read_csv to read Top 5000 songs from tsort.info, with convenient defaults (url, file name, NA encoding).

**tsm_read_albums()**: Wrapper around readr::read_csv to read Top 3000 albums from tsort.info, with convenient defaults.

**tsm_read_chart()**: Wrapper around readr::read_csv to read full chart data from tsort.info, with convenient defaults.

**tsm_get_version()** retrieves the current version of the data at https://tsort.info/ as noted at this web address:

https://tsort.info/music/faq_version_numbers.htm


## Customized plotting

The following plotting functions are available:

**tsm_ggbox(data)**: ggplot2 boxplot additionally showing original data points using a slightly customized theme based on theme_bw().

tsm_ggbox(albums)

**tsm_ggbox_plotly(p)**: interactive plotly diagram showing mouse-over information.

p <- tsm_ggbox(albums)  
tsm_ggbox_plotly(p)

## Usage

```{r usage, include = TRUE, fig.width = 6, fig.height = 5}

tsm_get_version()

albums <- tsm_read_albums()
attr(albums, "version")

tsm_ggbox(albums)

```

You can make an interactive plotly chart like so (not carried out here because of file sizes):
  
`p <- tsm_ggbox(albums)`
`tsm_ggbox_plotly(p)`
