---
title: "Intro to tsortmusicr"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Intro_to_tsortmusicr}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(tsortmusicr)
```

This is a package designed to help explore data from the great website https://tsort.info/.

Note that usage of data from tsort.info is free under the following conditions:

1. Acknowledge the source.

2. Prominently link to https://tsort.info

3. Always include version number.


The following functions are available:

**tsm_read_songs()**: Wrapper around readr::read_csv to read Top 5000 songs from tsort.info, with convenient defaults (url, file name, NA coding).

**tsm_read_albums()**: Wrapper around readr::read_csv to read Top 3000 albums from tsort.info, with convenient defaults.

**tsm_read_chart()**: Wrapper around readr::read_csv to read full chart data from tsort.info, with convenient defaults.

**tsm_get_version()** retrieves the current version of the data at https://tsort.info/ as noted at this web address:

https://tsort.info/music/faq_version_numbers.htm

